Do NBA Teams Avoid Trading within Their Own Division?^[We appreciate feedback we received on this paper from Skye Bender-deMoll, Pavel Krivitsky and David Schaefer.]

### 2022-01-06 Manuscript.Rmd
Fix year in funnel plot legend

```{r seasonal-ergms, fig.cap="**Homophily Coefficients and Standard Errors from Weighted Exponential Random Graph Models.** (including base-rate effects)"}
with(
  readRDS("ergm-seasonal-db.rds") %>%
    mutate(
      season_start = as.numeric(substr(season, 1, 4))
    ) %>%
    filter( 
      model_name == "B", 
      term == "nodematch.sum.division",
      season_start < 2019
    ),
  metafor::funnel(estimate, vi = std.error^2, 
                  col = c("black", "red")[(season_start > 2004) + 1]
  )
)
legend(
  "topright",
  pch = 19,
  col = c("black", "red"),
  legend = c("1976 - 2004", "2004 - 2019")
)

```

>>>>

```{r seasonal-ergms, fig.cap="**Homophily Coefficients and Standard Errors from Weighted Exponential Random Graph Models.** (including base-rate effects)"}
with(
  readRDS("ergm-seasonal-db.rds") %>%
    mutate(
      season_start = as.numeric(substr(season, 1, 4))
    ) %>%
    filter( 
      model_name == "B", 
      term == "nodematch.sum.division",
      season_start < 2019
    ),
  metafor::funnel(estimate, vi = std.error^2, 
                  col = c("black", "red")[(season_start > 2004) + 1]
  )
)
legend(
  "topright",
  pch = 19,
  col = c("black", "red"),
  legend = c("1976 - 2004", "2005 - 2019")
)
```
